Dismal Code: Studying the Evolution of Security Bugs

### 2013-04-02 docs/evol.tex
info about Maven - minor changes

One of the most common approaches to identify security bugs is
{\it static analysis}~\cite{CW07}. This kind of analysis involves the
inspection of the program's source or object code without executing
it. For our research we used {\it FindBugs},\footnote{\url{http://findbugs.sourceforge.net/}}
a static analysis tool that examines bytecode to detect software bugs and has already been used in
research~\cite{AP10}\cite{HP07}\cite{HP04}\cite{HW08}. Specifically, we ran FindBugs on all the project
versions of all the projects that exist in the Maven\footnote{\url{http://maven.apache.org/}}
repository (approximately 265GB of data). Then we observed the changes that
involved the security bugs and their characteristics. This research builds upon
our earlier work on the topic~\cite{MGS12}.

@@

The main contributions of this research are:
\begin{itemize}
	\item The analysis of how security bugs evolve over time. To achieve
this, we inspect every project per version. Our hypothesis is that security
bugs must decrease as a project evolves since they are critical and developers
should eliminate them.
	\item Security bug persistense between versions. We show evidence that
security bugs are not eliminated between versions.
	\item We show evidence of the relation between security bugs and a project
version's size.  Here, size is defined in terms of bytecode.
	\item The correlation of security bugs with other bug categories. We
show evidence on how such bugs are correlated with bugs that have to do with
performance, coding practices and others.
%	\item The relation of software dependencies and security bugs. Our
%hypothesis is that an artifact that is a dependency of many other artifacts
%should have a low rate of security bugs. 
\end{itemize}

@@

Our experiment involved the collection of the metric results of the FindBugs
tool. Before and during the experiment, we performed a number of functional
fits on the data for reasons that we will describe below.

@@

Our experiment involved four entities (see Table~\ref{tbl:exp}):
a number of {\it workers}, a {\it task queue}
mechanism,\footnote{\url{http://www.rabbitmq.com/}}
a {\it data repository},\footnote{\url{http://www.mongodb.org/}}
and the {\it code repository}, which in our case it was the public Maven 
repository\footnote{\url{http://mvnrepository.com}}.

\begin{table}
\centering
\caption{Experiment Entities}
\label{tbl:exp}
\begin{tabular}{r r r}
\hline
Entity & Software Package & Version\\
\hline
Worker & Custom Python Script & 2.7\\
Task Queue & RabbitMQ & 3.0.1 \\
Data Repository & MongoDB & 2.2 \\
Code Repository & Maven Repository & January 2012 \\
\hline
\end{tabular}
\end{table}

@@

A typical processing cycle of a worker included the following steps: after
the worker spawned, it requested a task from the queue. This task contained
the {\sc jar} name, which was typically a project version that was downloaded locally.
First, specific {\sc jar} metadata were calculated and stored. Such metadata included
its size, its dependencies, and a number that represented the chronological order of the
release. This order was derived from an {\sc xml} file that
accompanies every project in the Maven repository called {\it
maven-metadata.xml}. Then, FindBugs was executed and its results were also stored
in the data repository. When the task was completed the queue was notified and
the next task was requested.

@@

>>>>

One of the most common approaches to identify security bugs is
{\it static analysis}~\cite{CW07}. This kind of analysis involves the
inspection of the program's source or object code without executing
it. For our research we used {\it FindBugs},\footnote{\url{http://findbugs.sourceforge.net/}}
a static analysis tool that examines bytecode to detect software bugs and has already been used in
research~\cite{AP10}\cite{HP07}\cite{HP04}\cite{HW08}. Specifically, we ran FindBugs on all the project
versions of all the projects that exist in the
{\it Maven Central Repository}\footnote{\url{http://search.maven.org/}}
(approximately 265GB of data). Then we observed the changes that
involved the security bugs and their characteristics. This research builds upon
our earlier work on the topic~\cite{MGS12}.

@@

The main contributions of this research are:
\begin{itemize}
	\item The analysis of how security bugs evolve over time. To achieve
this, we inspect every project per version. Our hypothesis is that security
bugs must decrease as a project evolves since they are critical and developers
should eliminate them.http://search.maven.org/
	\item Security bug persistense between versions. We show evidence that
security bugs are not eliminated between versions.
	\item We show evidence of the relation between security bugs and a project
version's size.  Here, size is defined in terms of bytecode.
	\item The correlation of security bugs with other bug categories. We
show evidence on how such bugs are correlated with bugs that have to do with
performance, coding practices and others.
%	\item The relation of software dependencies and security bugs. Our
%hypothesis is that an artifact that is a dependency of many other artifacts
%should have a low rate of security bugs. 
\end{itemize}

@@

Our experiment involved the collection of the metric results of the FindBugs
tool. Before and during the experiment, we performed a number of functional
fits on the data coming from the Maven repository,
http://search.maven.org/for reasons that we will describe below.

@@

Our experiment involved four entities (see Table~\ref{tbl:exp}):
a number of {\it workers}, a {\it task queue}
mechanism, a {\it data repository}, and the {\it code repository},
which in our case it was the public Maven repository.

\begin{table}
\centering
\begin{threeparttable}
\caption{Experiment Entities}
\label{tbl:exp}
\begin{tabular}{l r r}
\hline
Entity & Software Package & Version\\
\hline
Worker & Custom Python Script & 2.7\\
Task Queue & RabbitMQ\tnote{1} & 3.0.1 \\
Data Repository & MongoDB\tnote{2} & 2.2 \\
Code Repository & Maven Central Repository\tnote{3} & January 2012 \\
\hline
\end{tabular}
 \begin{tablenotes}
       	\item[1] \url{http://www.rabbitmq.com/}
       	\item[2] \url{http://www.mongodb.org/}
	\item[3] \url{http://mvnrepository.com}
   \end{tablenotes}
\end{threeparttable}
\end{table}

@@

A typical processing cycle of a worker included the following steps: after
the worker spawned, it requested a task from the queue. This task contained
the {\sc jar} name, which was typically a project version that was downloaded locally.
First, specific {\sc jar} metadata were calculated and stored. Such metadata included
its size, its dependencies, and a number that represented the chronological order of the
release. This order was derived from an {\sc xml} file that
accompanies every project in the Maven repository called {\it
maven-metadata.xml}. Then, FindBugs was invoked by the worker and its results were
also stored in the data repository. When the task was completed the queue
was notified and the next task was requested.

@@

Maven is a build automation tool used primarily for Java projects and it is
hosted by the Apache Software Foundation.\footnote{\url{http://www.apache.org/}}
To describe the software project being built, its dependencies
on other external modules, the build order, and required plug-ins Maven uses
{\sc xml}. To build a software component, it dynamically downloads Java libraries
and Maven plug-ins from the Maven Central Repository,
and stores them in a local cache. The repository can also be updated with new
new projects but also with new versions of existing ones.
